Guarded Recursion in Agda via Sized Types

### 2019-01-31 code-oneclock-paper/latex/Introduction.tex
Added overview of paper

>>>>

The remainder is organized as follows.
We discuss the meta-theory and recall sized types in \Cref{sec:prelim}.
Then we give the syntax of guarded recursive type theory \Cref{sec:syntax}.
In \Cref{sec:presheaf_sem,sec:guarded}, we define a denotational semantics of the syntax using sized types.  
For that, we first define a presheaf model and give the Kripke semantics, and then we show how to interpret the additional type and term formers of guarded recursive type theory.
Finally, we conclude that the syntax is consistent in \Cref{sec:consistent}.
